Make a Map for our Paper

### 2025-03-24 001-map-of-samples.Rmd
Make run types different shapes on the map

mm <- base_map + 
  geom_segment(data = labels, aes(x = tip_long, y = tip_lat, xend = label_long, yend = label_lat), colour = "black", linewidth = 0.4) +
  geom_point(data = labels, aes(x = label_long + bit + (1 - hjust * 2) * kick * (rank - 1), y = label_lat, fill = run_timing), shape = 21, size = 3.5) +
  geom_label(
    data = labels_1line,
    aes(
      x = label_long + bit + (1 - hjust * 2) * kick * ( 0.65 + rank - 1),
      y = label_lat, 
      label = map_text,
      hjust = hjust
    ),
    size = 2.2,
    label.padding = unit(0.09, "lines"),
    lineheight = 0.85
  ) +
  scale_fill_manual(values = run_time_colors) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", linewidth = 1),
    axis.text.x = element_text(size = 8, family = "serif", angle = 35, hjust = 1),
    axis.text.y = element_text(size = 8, family = "serif"),
    axis.title.y = element_text(family = "serif", size = 10),
    axis.title.x = element_text(family = "serif", vjust = 2, size = 10),
    plot.margin = margin(0, 0.1, 0, 0.15, "cm"),
    legend.position = "none"
  ) +
  xlab("Longitude") +
  ylab("Latitude") +
  coord_sf(
    expand = FALSE,
  ) +
  guides(fill = guide_legend(title = "Run Timing:", nrow = 2)) +
  ggspatial::annotation_north_arrow(location = "br", height = unit(10, "mm"), width = unit(5, "mm"), style = north_arrow_fancy_orienteering()) +
  ggspatial::annotation_scale(location = "br", height = unit(0.1, "cm"))

@@

file.copy(from = output_list$cropmap, to = output_list$texmap)

@@

for(r in 1:nrow(rc_col_tib)) {
  tmp <- rc_col_tib[r,]
  g <- ggplot(tmp, aes(x = 1, y = 1)) +
    geom_point(shape = 21, fill = tmp$value, size = 3.5) +
    theme_void()
  ggsave(g, filename = tmp$file)

>>>>

# define the shapes
point_shapes <- c(
  `Fall run` = 21,
  `Spring run` = 22,
  `Winter run` = 23,
  `Late-fall run` = 24
)

mm <- base_map + 
  geom_segment(data = labels, aes(x = tip_long, y = tip_lat, xend = label_long, yend = label_lat), colour = "black", linewidth = 0.4) +
  geom_point(data = labels, aes(x = label_long + bit + (1 - hjust * 2) * kick * (rank - 1), y = label_lat, fill = run_timing, shape = run_timing), size = 3.5) +
  geom_label(
    data = labels_1line,
    aes(
      x = label_long + bit + (1 - hjust * 2) * kick * ( 0.65 + rank - 1),
      y = label_lat, 
      label = map_text,
      hjust = hjust
    ),
    size = 2.2,
    label.padding = unit(0.09, "lines"),
    lineheight = 0.85
  ) +
  scale_fill_manual(values = run_time_colors) +
  scale_shape_manual(values = point_shapes) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", linewidth = 1),
    axis.text.x = element_text(size = 8, family = "serif", angle = 35, hjust = 1),
    axis.text.y = element_text(size = 8, family = "serif"),
    axis.title.y = element_text(family = "serif", size = 10),
    axis.title.x = element_text(family = "serif", vjust = 2, size = 10),
    plot.margin = margin(0, 0.1, 0, 0.15, "cm"),
    legend.position = "none"
  ) +
  xlab("Longitude") +
  ylab("Latitude") +
  coord_sf(
    expand = FALSE,
  ) +
  guides(fill = guide_legend(title = "Run Timing:", nrow = 2)) +
  ggspatial::annotation_north_arrow(location = "br", height = unit(10, "mm"), width = unit(5, "mm"), style = north_arrow_fancy_orienteering()) +
  ggspatial::annotation_scale(location = "br", height = unit(0.1, "cm"))

@@

file.copy(from = output_list$cropmap, to = output_list$texmap, overwrite = TRUE)

@@

for(r in 1:nrow(rc_col_tib)) {
  tmp <- rc_col_tib[r,]
  g <- ggplot(tmp, aes(x = 1, y = 1)) +
    geom_point(shape = point_shapes[tmp$name], fill = tmp$value, size = 3.5) +
    theme_void()
  ggsave(g, filename = tmp$file)
